---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SABCplot

<!-- badges: start -->
<!-- badges: end -->

The goal of SABCplot is a quantitative statistical graph for evaluating the MTE using BFs and S-values while accounting for estimation precision. The information required to construct the S-ABC plot consists solely those of factors for the point estimate of the effect measure, its standard error, and the researcher’s specified hypotheses reported within the paper.

## Installation

You can install the development version of SABCplot from [GitHub](https://github.com/takagi6u/SABCplot.git) .

``` r
# install.packages("pak")
pak::pak("takagi6u/SABCplot")

# Or using remotes
# install.packages("remotes")
remotes::install_github("takagi6u/SABCplot")
```

## Example

This is a basic example which shows you how to solve a common problem. Suppose you have a study where the primary endpoint is the difference in means between two groups, and you have a point estimate, its standard error, sample size (N1 and N2). The hypotheses you want to know are a minimum treatment effect (mte) of 8, an assumed treatment effect using a sample size calculation (ate) of 58, and a zero treatment effect (zte) of 0. If both mte and ate are available, select "composite" for BF_type.

```{r example1}
library(SABCplot)

estimate <- 16.7
se <- 6.336172
N1 <- 95  
N2 <- 95

SABCplot(effect_measure = "difference in means"
         , BF_type = "composite"
         , estimate = estimate
         , stderr = se
         , N1 = N1
         , N2 = N2
         , zte = 0
         , ate = 58
         , mte = 8
         , conf_levels = c(0.95)
         , low_axes = -10
         , upp_axes = 70
         , length_axes = 10)
 
```

From this information, an S-ABC plot can be drawn. Optionally, you can plot graphs based on both zte and ate hypotheses by changing the BF hypothesis settings. Enter zte and ate, and select "Simple" as the BF_type. You can also increase the confidence interval you want to see. Enter the confidence coefficient you want to see in conf_levels. You can choose effect_measure from effect measures commonly used in clinical trials, such as "difference in means", "risk difference", "log risk ratio", "log odds ratio", and "log hazard ratio".

```{r example2}

library(SABCplot)

estimate <- 16.7
se <- 6.336172
N1 <- 95  
N2 <- 95

SABCplot(effect_measure = "difference in means"
         , BF_type = "simple"
         , estimate = estimate
         , stderr = se
         , N1 = N1
         , N2 = N2
         , zte = 0
         , ate = 58
         , conf_levels = c(0.8, 0.95)
         , low_axes = -10
         , upp_axes = 70
         , length_axes = 10)
```
